\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-05-15 reviews/response.Rmd

---
title: Response to reviewers
author: JCGS-18-293
output:
  MonashEBSTemplates::memo:
    includes:
      in_header: preamble2.tex
fontfamily: mathpazo
---

We thank the reviewers for their helpful feedback which has led to many improvements in the paper. The point by point description of changes are below: the reviewers' comments are in red and our response is in black.

In addition, we have expanded the paper by including a subsection titled "2.4 Reasons to use calendar-based graphics" to explain why to use calendar plots, and a short section titled "3 Making calendar facets" which describes a new function `facet_calendar()`, that extends **ggplot2** intervals and complements the existing function `frame_calendar()`. It allows this algorithm to integrate more deeply with the **ggplot2** architecture.

@@

# Reviewer 1 comments {-}

> Figure 2 and Figure 10 show much the same information. You can see the Australian Open period in both. There is more detail in Figure 10 for the State Library.  The gaps in the Birrarung Marr data are easier to see in Figure 2.

We have explained the purpose of showing both displays in the revised paper, by including a new subsection "2.4 Reasons to use calendar-based graphics" to explain why to use calendar plots, and what information is typically revealed by calendar plots but not by other plots. The calendar display doesn't replace traditional displays, but serves to complement them to further tease out interesting structures in the data.

### 2019-05-15 main.Rmd
separate fig caption from fig chunk

```{r boxplot, fig.height = 8, fig.cap = "Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased variability is noted on the last day of December as approaching towards New Year's Eve.", fig.show = "hide"}
```

@@

```{r hod, fig.height = 6, fig.cap = "Scatterplots of half-hourly energy usage by time of day, with hourly averages overlaid, faceted by household and type of day. All households have different week days versus weekends daily routines. On week days, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning is notable in households 1 and 2, as seen by horizontal clusters of points."}
```

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy comsumption by household 2 is visible in January and February."}
```

@@

```{r h1, fig.height = 7, fig.cap = "The calendar display for household 1 indicates higher weekend usage and higher usage in the summer months (November-February). It seems that this household took a vacation in June.", eval = FALSE}
```

```{r h2, fig.height = 7, fig.cap = "The calendar display for household 2 reveals their tendency to use air conditioning and heating continuously. Some vacation days were taken in late December and in the second week of June.", eval = FALSE}
```

```{r h3, fig.height = 7, fig.cap = "The calendar display for household 3 reveals higher energy use in the winter months (May-August), with multiple peaks daily on both week days and weekends. There are some high peaks in summer (November-February), perhaps indicating occasional air conditioner use. There have been several long vacations in the past year.", eval = FALSE}
```

```{r h4, fig.height = 7, fig.cap = "The calendar display for household 4 shows energy use mostly in the evenings and on weekends. Four short trips were taken in October, December, April, and June.", eval = FALSE}
```

>>>>

@@

```{r hod, fig.height = 6, fig.cap = "(ref:hod-cap)"}
```

(ref:hod-cap) Scatterplots of half-hourly energy usage by time of day, with hourly averages overlaid, faceted by household and type of day. All households have different week days versus weekends daily routines. On week days, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning is notable in households 1 and 2, as seen by horizontal clusters of points.

```{r calendar-elec, fig.height = 10.5, fig.cap = "(ref:calendar-elec-cap)"}
```

(ref:calendar-elec-cap) Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy consumption by household 2 is visible in January and February.

@@

### 2019-05-15 main.tex
separate fig caption from fig chunk

\caption{Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy comsumption by household 2 is visible in January and February.}\label{fig:calendar-elec}
\end{figure}

>>>>

\caption{Calendar displays faceted by each household using global scales. Long flat low energy usage indicates vacation time, and high energy consumption by household 2 is visible in January and February.}\label{fig:calendar-elec}
\end{figure}
